Graph-Based Neural Reconstruction from Morphological Skeletons

### 2017-11-15 papers/cvpr2018/0_introduction.tex
Further cleanup.

This work makes the following following contributions: (1) a novel top-down graph-based method for neural reconstruction of connectomics data; (2) a region-based CNN classifier to detect errors under global constraints; (3) an empirical evaluation of our method on several connectomics datasets; (4) our method yields improved performance over the state-of-the-art on X out of Y datasets, and competitive results on the remaining data. On average, we improve the Variation of Information (VI) metric across all datasets by X percent without drastically increasing the running time.

>>>>

This work makes the following following contributions: (1) a novel top-down graph-based method for neural reconstruction of connectomics data; (2) a region-based CNN classifier to detect errors under global constraints; (3) an empirical evaluation of our method on several connectomics datasets; (4) our method yields improved performance over the state-of-the-art on \FIX{X out of Y} datasets, and competitive results on the remaining data. On average, we improve the Variation of Information (VI) metric across all datasets by \FIX{X} percent without drastically increasing the running time.

### 2017-11-15 papers/cvpr2018/2_method.tex
Further cleanup.

There are two types of errors that can occur in connectomics segmentation.
The first, called a split error, occurs when there are two segments that should have been merged. The second, called a merge error, happens when one segment should be split into two. Generally, it is much more difficult to correct merge errors than to correct split errors,
as the space of possible split proposals grow quickly~\cite{parag2015properties},.
Thus, most reconstruction approaches are tuned towards over-segmentation with many more split than merge errors. Our method takes as input over-segmentations of EM image volumes generated by state-of-the-art connectomics reconstruction pieplines (Sec.~\ref{sec:neuroproof}). Our goal is to identify locations of split errors and merge the corresponding segments automatically.

From the input segmentation we generate a graph $G$ with nodes $N$ and edges $E$ with non-negative edge weights $w_e$. The nodes correspond to label segments from the segmentation with edges between segments considered for merging. Ideally, our graph has edges corresponding to all of the segments that were erroneously split. To compute this graph we generate a skeleton for every segment in the pixel-based segmentation. The skeleton is a simplified representation of the overall shape of the neurons. From this skeleton we  identify potential merge locations and produce the corresponding edges for the graph. To find actual merges we run a classification CNN to generate edge weights that correspond to probabilites of merging. We then use a multicut heuristic to generate a partition on the graph where nodes in the same partition are assigned the same output label in the improved segmentation. We will now discuss the three major components to our framework (graph creation, edge weights assignment, and graph partitioning) in more detail.

\subsection{Graph Creation}
\label{sec:skeletonization}
\donglai{need some overview sentence}
%We generate nodes $N$ and edges $E$ to apply a graph-based optimization strategy for segmentation.
%In addition, these edges receive non-negative weights.

\subsubsection{Node Generation}

@@

\subsubsection{Edge Generation}

>>>>

There are two types of errors that can occur in connectomics segmentation.
The first, called a split error, occurs when there are two segments that should have been merged. The second, called a merge error, happens when one segment should be split into two. Generally, it is much more difficult to correct merge errors than to correct split errors,
as the space of possible split proposals grow quickly~\cite{parag2015properties}.
Thus, most reconstruction approaches are tuned towards over-segmentation with many more split than merge errors. Our method takes as input over-segmentations of EM image volumes generated by state-of-the-art connectomics reconstruction pieplines (Sec.~\ref{sec:neuroproof}). Our goal is to identify locations of split errors and merge the corresponding segments automatically.

From the input segmentation we generate a graph $G$ with nodes $N$ and edges $E$ with non-negative edge weights $w_e$. The nodes correspond to label segments from the segmentation with edges between segments considered for merging. Ideally, our graph has edges corresponding to all of the segments that were erroneously split. To compute this graph we generate a skeleton for every segment in the pixel-based segmentation. The skeleton is a simplified representation of the overall shape of the neurons. From this skeleton we  identify potential merge locations and produce the corresponding edges for the graph. To find actual merges we run a classification CNN to generate edge weights that correspond to probabilities of merging. We then use a multicut heuristic to generate a partition on the graph where nodes in the same partition are assigned the same output label in the improved segmentation. We will now discuss the three major components to our framework (graph creation, edge weights assignment, and graph partitioning) in more detail.

%\subsection{Graph Creation}

\donglai{need some overview sentence}
%We generate nodes $N$ and edges $E$ to apply a graph-based optimization strategy for segmentation.
%In addition, these edges receive non-negative weights.

\subsection{Node Generation}
%\subsubsection{Node Generation}
\label{sec:skeletonization}

@@

\subsection{Edge Generation}

### 2017-11-15 papers/cvpr2018/3_evaluation.tex
Further cleanup.

\noindent\textbf{Kasthuri.}
The Kasthuri dataset consists of scanning electron microscope images of the neocortex of a mouse brain~\cite{kasthuri2015saturated}. This dataset is $5342 \times 3618 \times 338$ voxels in size. The resolution of the dataset is $\SI[product-units=single]{3 x 3 x 30}{\nano\meter}^3$ per voxel. We evaluate our methods using the left cylinder of this 3-cylinder dataset. We downsample the dataset in the $x$ and $y$ dimensions to give a final resolution of $\SI[product-units=single]{6 x 6 x 30}{\nano\meter}^3$ per voxel. We divide the dataset into two volumes (Vol. 1 and Vol. 2) along the $x$ dimension where each volume is $\SI[product-units=single]{8.0 x 10.9 x 10.1}{\micro\meter}^3$.

\noindent\textbf{FlyEM.}
The FlyEM dataset comes from the mushroom body of a 5-day old adult male Drosophila fly imaged by a focused ion-beam milling scanning electron microscopy~\cite{takemura2017connectome}. The mushroom body in this species is the major site of associative learning. The original dataset contains a $\SI[product-units=single]{40 x 50 x 120}{\micro\meter}^3$ volume of which we use two cubes of size $\SI[product-units=single]{10 x 10 x 10}{\micro\meter}^3$. The resolution of this dataset is $\SI[product-units=single]{10 x 10 x 10}{\nano\meter}^3$ or $1000$ voxels in each dimension in each of the two volumes.

>>>>

\paragraph{Kasthuri.}
The Kasthuri dataset consists of scanning electron microscope images of the neocortex of a mouse brain~\cite{kasthuri2015saturated}. This dataset is $5342 \times 3618 \times 338$ voxels in size. The resolution of the dataset is $\SI[product-units=single]{3 x 3 x 30}{\nano\meter}^3$ per voxel. We evaluate our methods using the left cylinder of this 3-cylinder dataset. We downsample the dataset in the $x$ and $y$ dimensions to give a final resolution of $\SI[product-units=single]{6 x 6 x 30}{\nano\meter}^3$ per voxel. We divide the dataset into two volumes (Vol. 1 and Vol. 2) along the $x$ dimension where each volume is $\SI[product-units=single]{8.0 x 10.9 x 10.1}{\micro\meter}^3$.

\paragraph{FlyEM.}
The FlyEM dataset comes from the mushroom body of a 5-day old adult male Drosophila fly imaged by a focused ion-beam milling scanning electron microscopy~\cite{takemura2017connectome}. The mushroom body in this species is the major site of associative learning. The original dataset contains a $\SI[product-units=single]{40 x 50 x 120}{\micro\meter}^3$ volume of which we use two cubes of size $\SI[product-units=single]{10 x 10 x 10}{\micro\meter}^3$. The resolution of this dataset is $\SI[product-units=single]{10 x 10 x 10}{\nano\meter}^3$ or $1000$ voxels in each dimension in each of the two volumes.

### 2017-11-15 papers/cvpr2018/paper.tex
Further cleanup.

\def\cvprPaperID{0446} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
%
\newcommand{\hp}[1]{\textcolor{red}{HP: #1}}
\newcommand{\donglai}[1]{\textcolor{blue}{[Donglai: #1]}}

@@

%%%%%%%%% ABSTRACT
\begin{abstract}
Advancements in electron microscopy image acquisition have created massive connectomics datasets in the terabyte range that make manual reconstruction of neuronal structures infeasible. 
Current state-of-the-art automatic methods segment neural membranes at the pixel level followed by agglomeration methods to create full neuron reconstructions. 
However, these approaches widely neglect global geometric properties that are inherent in the graph structure of neural wiring diagrams.
In this work, we follow bottom-up pixel-based reconstruction by a top-down graph-based method to more accurately approximate neural pathways. 
Using the membrane labels of the pixel-based segmentation we first generate skeletons in 3D.
Using this 3D graph we train automatic classifiers for shape description to detect impossible neural pathways by looking at geometric properties.
We then apply efficient graph-based optimization strategies to improve the segmentation labels. We demonstrate the performance of our approach on multiple real-world connectomics datasets with average variation of information improvement of $X\times$. 
%The paper provides insights into learning shape features for top-down graph-based neuron reconstruction.
\end{abstract}
%%%%%%%%	% BODY TEXT

>>>>

\def\cvprPaperID{0446} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
%
\newcommand{\FIX}[1]{\textcolor{red}{#1}}
\newcommand{\hp}[1]{\textcolor{red}{HP: #1}}
\newcommand{\donglai}[1]{\textcolor{blue}{[Donglai: #1]}}

@@

%%%%%%%%% ABSTRACT
\begin{abstract}
Advancements in electron microscopy image acquisition have created massive connectomics datasets in the terabyte range that make manual reconstruction of neuronal structures infeasible. 
Current state-of-the-art automatic methods segment neural membranes at the pixel level followed by agglomeration methods to create full neuron reconstructions. 
However, these approaches widely neglect global geometric properties that are inherent in the graph structure of neural wiring diagrams.
In this work, we follow bottom-up pixel-based reconstruction by a top-down graph-based method to more accurately approximate neural pathways. 
Using the membrane labels of the pixel-based segmentation we first generate skeletons in 3D.
Using this 3D graph we train automatic classifiers for shape description to detect impossible neural pathways by looking at geometric properties.
We then apply efficient graph-based optimization strategies to improve the segmentation labels. We demonstrate the performance of our approach on multiple real-world connectomics datasets with average variation of information improvement of \FIX{$X\times$}. 
%The paper provides insights into learning shape features for top-down graph-based neuron reconstruction.
\end{abstract}
%%%%%%%%	% BODY TEXT
